### 2023-08-13 paper/image/累积归一化连接性.tex
initialize

\begin{figure}[ht]
    \centering
    % 也可以考虑使用minipage单纯的并排(不考虑子编号)
    \begin{subfigure}[t]{0.46\textwidth}
        \centering
        \includegraphics[width=\linewidth , height=0.6\linewidth]{../../images/ANC_CN_9.png}
        \caption{}
        \label{fig:1a}
    \end{subfigure}
    \begin{subfigure}[t]{0.46\textwidth}
        \centering
        \includegraphics[width=\linewidth , height=0.6\linewidth]{../../images/ANC_ND_9.png}
        \caption{}
        \label{fig:1b}
    \end{subfigure}
    \caption{累积归一化连接性}
    \label{fig:累积归一化连接性}
\end{figure}